News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-12-30 rupnik2015.tex
acknowledgments added
ack revised

\documentclass[twoside,11pt]{article}
\usepackage{jair, theapa, rawfonts}
\usepackage{pgfplots}
%\usepackage{graphicx}

@@

%\acks{The authors wish to thank blah blah blah.}

>>>>

\documentclass[twoside,11pt]{article}
\usepackage{jair, theapa, rawfonts, url}
\usepackage{pgfplots}
%\usepackage{graphicx}

@@

\acks{The authors gratefully acknowledge that the funding for this work was provided by the projects X-LIKE (ICT-257790-STREP), MultilingualWeb (PSP-2009.5.2 Agr.\# 250500), TransLectures (FP7-ICT-2011-7), PlanetData (ICT-257641-NoE), RENDER (ICT-257790-STREP), XLime (FP7-ICT-611346), and META-NET (ICT-249119-NoE).}
